Technical Report

### 2018-06-18 fully-abstract-comp/technical-report.tex
made a claim more precise

    \lau{At this point we would like to use the IH, but we do not have $R_W'(a) \uplus W_M$ defined as $R_W'(a)$ is a split of $W_M$.}

>>>>

    \lau{At this point we would like to use the IH, but we do not have $R_W'(a) \uplus W_M$ defined because $R_W'(a)$ is a split of $W_M$ (in the case where the capability is $\linear$, in the other case we are fine.).}
